merge conflict II
    Let’s say you decide you’d like to merge the changes from fencing into master.

    Here’s where the trouble begins!

    You’ve made commits on separate branches that alter the same line in conflicting ways. Now, when you try to merge fencing into master, Git will not know which version of the file to keep.

Instructions
    1.
    Switch to the master branch.

    2.
    From the terminal, enter the command below:
        git merge fencing
    
    This will try to merge fencing into master.

    In the output, notice the lines:
        CONFLICT (content): Merge conflict in resumé.txt
        Automatic merge failed; fix conflicts and then commit the result.

    3.
    We must fix the merge conflict.

    In the code editor, look at resume.txt. Git uses markings to indicate the HEAD (master) version of the file and the fencing version of the file, like this:
        <<<<<<< HEAD
        master version of line
        =======
        fencing version of line
        >>>>>>> fencing

    Note: If the markings are not showing in resume.txt, please close resume.txt and re-open via the folder icon at the top left corner of the editor.

    Git asks us which version of the file to keep: the version on master or the version on fencing. You decide you want the fencing version.

    From the code editor:
        Delete the content of the line as it appears in the master branch
    
        Delete all of Git’s special markings including the words HEAD and fencing. If any of Git’s markings remain, for example, >>>>>>> and =======, the conflict remains.

    4.
    Add resume.txt to the staging area.

    5.
    Now, make a commit. For your commit message, type “Resolve merge conflict” to indicate the purpose of the commit.

    Here’s a hint for the commit command.